\begin{thebibliography}{99.}

\bibitem{g-stock-01} Chokesatean, P.: Credibility-based Binary Feedback Model for Grid Resource Planning. University of Pittsburgh (2008)

\bibitem{mql5-cloud-network-01} Chang, C., Narayana Srirama S., Buyya, R.: Indie Fog An Efficient Fog-Computing Infrastructure for the Internet of Things. Computer \textbf{50}(9), 92--98 (2017)

\bibitem{money-bee-01} Bohn, A., Guting, T., Mansmann, T.: MoneyBee Aktienkursprognose mit kunstlicher intelligenz bei hoher rechenleistung. Wirtschaftsinf \textbf{45}, 325--333 (2003)

\bibitem{genetic-algorithms-01} Donate, J.P., Li, X., Sanchez, G.G., Miguel, A.S.: Time series forecasting by evolving artificial neural networks with genetic algorithms, differential evolution and estimation of distribution algorithm. Neural Computing and Applications \textbf{22}, 11--20 (2013)

\bibitem{time-series-01} Bandt, C., Pompe, B.: Permutation Entropy A Natural Complexity Measure for Time Series. Physical Review Letters, \textbf{88}(17), 174102 (2002)

\bibitem{time-series-02} Salvador, S., Chan, P.: Toward Accurate Dynamic Time Warping in Linear Time and Space. Intelligent Data Analysis, \textbf{11}(5) 561--580 (2007)

\bibitem{time-series-03} Lan, Y.: Computational Approaches for Time Series Analysis and Prediction Data-Driven Methods for Pseudo-Periodical Sequences. University of Bradford (2009)

\bibitem{vitosha-trade-01} Zankinski, I., Barova, M., Tomov P.: Hybrid Approach Based on Combination of Backpropagation and Evolutionary Algorithms for Artificial Neural Networks Training by Using Mobile Devices in Distributed Computing Environment. Proceedings of Large-Scale Scientific Computing, 425--432 (2018)

\bibitem{distributed-computing-01} Megiddo, N.: Applying parallel computation algorithms in the design of serial algorithms. Journal of the Association for Computing Machinery \textbf{30}(4), 852--865 (1983)

\bibitem{crowdsensing-01} Leppanen, T., Alvarez Lacasia, J., Tobe, Y., Sezaki, K., Riekki, J.: Mobile crowdsensing with mobile agents. Autonomous Agents and Multi-Agent Systems \textbf{31}, 1--35 (2017)

\bibitem{voting-01} Laukkanen, S., Kangas, A., Kangas, J.: Applying voting theory in natural resource management A case of multiple-criteria group decision support, Journal of Environmental Management, \textbf{64}(2), 127--137 (2002)

\end{thebibliography}
